%-------------------------
% Resume in Latex
% Author : Hilal Morrar
% Based off of: https://github.com/jakegut/resume
%------------------------

\documentclass[letterpaper,11pt]{article}

  \usepackage{latexsym}
  \usepackage[empty]{fullpage}
  \usepackage{titlesec}
  \usepackage{marvosym}
  \usepackage[usenames,dvipsnames]{color}
  \usepackage{verbatim}
  \usepackage{enumitem}
  \usepackage[hidelinks]{hyperref}
  \usepackage{fancyhdr}
  \usepackage[english]{babel}
  \usepackage{tabularx}
  \input{glyphtounicode}


  %----------FONT OPTIONS----------
  % sans-serif
  % \usepackage[sfdefault]{FiraSans}
  % \usepackage[sfdefault]{roboto}
  % \usepackage[sfdefault]{noto-sans}
  % \usepackage[default]{sourcesanspro}

  % serif
  % \usepackage{CormorantGaramond}
  % \usepackage{charter}


  \pagestyle{fancy}
  \fancyhf{} % clear all header and footer fields
  \fancyfoot{}
  \renewcommand{\headrulewidth}{0pt}
  \renewcommand{\footrulewidth}{0pt}

  % Adjust margins
  \addtolength{\oddsidemargin}{-0.5in}
  \addtolength{\evensidemargin}{-0.5in}
  \addtolength{\textwidth}{1in}
  \addtolength{\topmargin}{-.5in}
  \addtolength{\textheight}{1.0in}

  \urlstyle{same}

  \raggedbottom
  \raggedright
  \setlength{\tabcolsep}{0in}

  % Sections formatting
  \titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large
  }{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

  % Ensure that generate pdf is machine readable/ATS parsable
  \pdfgentounicode=1

  %-------------------------
  % Custom commands
  \newcommand{\resumeItem}[1]{
    \item\small{
      {#1 \vspace{-2pt}}
    }
  }

  \newcommand{\resumeSubheading}[4]{
    \vspace{-2pt}\item
      \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{\small#3} & \textit{\small #4} \\
      \end{tabular*}\vspace{-7pt}
  }

  \newcommand{\resumeSubSubheading}[2]{
      \item
      \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textit{\small#1} & \textit{\small #2} \\
      \end{tabular*}\vspace{-7pt}
  }

  \newcommand{\resumeProjectHeading}[2]{
      \item
      \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \small#1 & #2 \\
      \end{tabular*}\vspace{-7pt}
  }

  \newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

  \renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

  \newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
  \newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
  \newcommand{\resumeItemListStart}{\begin{itemize}}
  \newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Hilal Morrar} \\ \vspace{1pt}
    \small 510-520-9271 $|$ \href{mailto:hilalmorrar@gmail.com}{\underline{hilalmorrar@gmail.com}} $|$ U.S. Citizen \\
    \href{https://www.linkedin.com/in/hilal-morrar/}{\underline{linkedin.com/in/hilal-morrar/}} $|$
    \href{https://github.com/hamorrar}{\underline{github.com/hamorrar}} $|$
    \href{https://hilalmorrar.com}{\underline{hilalmorrar.com/}} \end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
  
    \resumeSubheading{University of Texas at Austin}{August 2023 -- December 2024}{Masters of Science, Computer Science}{Austin, Texas}
      \resumeItemListStart
        \resumeItem{Coursework: Database Systems, Distributed Systems, Operating Systems, Prediction in Computer Architecture}
        % \resumeItem{Research Interest: Machine Learning and Systems}
    \resumeItemListEnd

    \resumeSubheading{University of California, Santa Cruz}{September 2018 -- June 2022}{Bachelors of Science, Computer Science}{Santa Cruz, CA}
      \resumeItemListStart
        \resumeItem{Cumulative GPA: 3.43, Dean's Honor List in Spring 2019, Summer 2020.}
        \resumeItem{Coursework: Algorithms, Artificial Intelligence, Data Structures, Machine Learning, Statistics}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    % \resumeSubheading{Software Engineer}{January 2025 -- Present}{Stealth Startup}{Remote}
    % \resumeItemListStart
    %   \resumeItem{Designing and Implementing various parts of the system from the ground up, including but not limited to UI, backend routes, database integration.}
    %   \resumeItem{Designing and Implementing various parts of the system from the ground up, including but not limited to UI, backend routes, database integration.}
    %   \resumeItem{Designing and Implementing various parts of the system from the ground up, including but not limited to UI, backend routes, database integration.}
    % \resumeItemListEnd

    \resumeSubheading{Software Engineer Intern}{May 2024 -- August 2024}{Cisco Systems - Duo Security}{Remote}
    \resumeItemListStart
      \resumeItem{Improved an internal performance testing tool by adding a feature using Python, AWS, and MySQL to dynamically create simulated customers and generate realistic HTTP requests.}
      \resumeItem{Executed load testing suites with GitHub CI/CD pipelines to monitor and validate software release performance metrics using Argo Workflows, Datadog, Grafana, and Kibana for observability and incident response.}
      \resumeItem{Diagnosed and fixed deployment issues in Kubernetes clusters and Docker containers, contributing to improved system reliability and reducing the risk of service degradation or on-call incidents.}
    \resumeItemListEnd

    \resumeSubheading{Computer Science Undergraduate Teaching Assistant}{September 2019 -- June 2022}{Baskin School of Engineering - Computer Science and Engineering Department}{Santa Cruz, CA}
      \resumeItemListStart
        \resumeItem{Developed tutoring curriculum for Applied Discrete Math, Computer Systems and Assembly Language, and Introduction to Python courses.}
        \resumeItem{Students consistently rated my sessions at least 8/10 and noticed an average grade increase of 9\%.}
        \resumeItem{Designed and graded weekly quizzes and Python assignments for Artificial Intelligence, Machine Learning courses.}
      \resumeItemListEnd

    \resumeSubheading{Machine Learning Engineer}{September 2020 -- August 2021}{Baskin School of Engineering - Computer Science and Engineering Department}{Santa Cruz, CA}
      \resumeItemListStart
        \resumeItem{Led the design and training efforts of various neural network model architectures to make predictions based on time-series data with PyTorch.}
        \resumeItem{Evaluated and tuned machine learning models using techniques like hyperparameter optimization, regularization, and pruning to achieve 95\% accuracy.}
        \resumeItem{Improved data processing pipeline to distribute model training in a Kubernetes GPU cloud cluster to reduce training time by 50\%.}
      \resumeItemListEnd
  
    \resumeSubheading{Frontend Software Engineer}{July 2020 -- September 2020}{Baskin School of Engineering - Computer Science and Engineering Department}{Santa Cruz, CA}
      \resumeItemListStart
        \resumeItem{Worked in an Agile team environment to build a device to monitor energy data in a residential network.}
        \resumeItem{Developed the frontend of a research lab website using React and JavaScript for UI/UX design.}
        \resumeItem{Connected frontend and backend to send, receive, and process user input for device registration via JSON.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading{\textbf{Distributed Key-Value Store} $|$ \emph{Go, Git, Docker}}{February 2023 -- Present}
      \resumeItemListStart
        \resumeItem{Developing the backend API of a distributed, fault tolerant, consistent, and sharded key-value store.}
        \resumeItem{Utilizing Goroutines for concurrency when handling client and internal HTTP requests for system communication.}
        % \resumeItem{Implementing a data hashing algorithm to broadcast data across multiple nodes equally.}
      \resumeItemListEnd

    % \resumeProjectHeading{\textbf{RustOS} $|$ \emph{Rust, Git}}{July 2023 -- Present}
    %   \resumeItemListStart
    %     \resumeItem{Building a simple Operating System in Rust as a way to take a project-based approach to learning the language.}
    %     \resumeItem{Implementing all basic parts of the system including CPU Interrupts, Memory Management, and Multitasking.}
    %   \resumeItemListEnd

    \resumeProjectHeading{\textbf{TagMe} $|$ \emph{Electron, Go, Git, Node.js, HTML/CSS}}{January 2022 -- March 2022}
      \resumeItemListStart
        \resumeItem{Worked in an Agile team to make a cross platform, full stack desktop application to search files by custom tags.}
        \resumeItem{Responsible for UI and frontend functionality, designed and implemented backend unit tests in Node.js.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}

  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Languages}{: Assembly, C, C++, Go, HTML/CSS, Java, JavaScript, Python} \\
      \textbf{Frameworks/Libraries}{: Agile, Gin, Keras, NumPy, PyTorch, React, TensorFlow, pandas, scikit-learn} \\
      \textbf{Developer Tools}{: Atlassian, Docker, Git, Jira, Jupyter Notebooks, Kubernetes, Linux/Unix, MySQL, PostgreSQL}}}
  \end{itemize}

\end{document}